R Tools for Obspack, Footprints and Receptors (rtorf)

### 2024-07-15 README.Rmd
fix #8

```{r, eval = F}
remotes::install_github("noaa-gml/rtorf")
```

```{r, include = T, message=F, warning=F}
library(rtorf)
library(data.table)
```

@@

```{r, eval = T}

@@

```{r}
df <- obs_read_nc(
  index = index,
  categories = "tower-insitu")

@@

```{r}
dft <- obs_table(df = df)
```

@@

```{r}
usites <- unique(df$site_name)[sample(seq_along(unique(df$site_name)), 2)]
usites
```

```{r}
knitr::kable(dft[site_name %in% usites])
```

@@

```{r, tidy = TRUE, dpi=300, fig.cap="First two sites in ObsPack"}
obs_plot(dt = df[site_name %in% usites], 
         time = "time", 
         yfactor = 1e9, 
         cex = 0.5,
         verbose = FALSE)
```

@@

```{r}
north <- 80
south <- 10
west <- -170
east <- -50
max_altitude <- 8000
evening <- 14

@@

```{r}
dfa <- df[,
          max(altitude_final),
          by = site_code] |> unique()

@@

```{r}
df2 <- obs_addtime(df)
```
Then we need a *key_time* to aggregate data.
This can be done using UTC, solar, or local time.
The normal approach is using afternoon solar or local time.

@@

```{r}
df2$solar_time <- obs_addstime(df2)

@@

```{r}
df2$solar_time_cut <- cut(x = df2$solar_time,
                          breaks = "1 hour") |>
  as.character()

@@

```{r}
df3 <- df2[hour_st %in% evening]
df3[, c("solar_time", "solar_time_cut")]

@@

```{r}
df3$key_time <- df3$solar_time_cut
```

```{r}
df4 <- obs_agg(dt = df3,
               gby = "mean",
               cols = c("value",
                        "latitude",
                        "longitude",
                        "site_utc2lst"),
               verbose = T,
               byalt = TRUE)
```

>>>>

```{r install, eval = F}
remotes::install_github("noaa-gml/rtorf")
```

```{r call, include = T, message=F, warning=F}
library(rtorf)
library(data.table)
```

@@

```{r read1, eval = T}

@@

```{r read2}
df <- obs_read_nc(
  index = index,
  categories = "tower-insitu")

@@

```{r table}
dft <- obs_table(df = df)
```

@@

```{r uniques}
usites <- unique(df$site_name)[sample(seq_along(unique(df$site_name)), 2)]
usites
```

```{r table1}
knitr::kable(dft[site_name %in% usites])
```

@@

```{r plot1, tidy = TRUE, dpi=300, fig.cap="First two sites in ObsPack"}
obs_plot(dt = df[site_name %in% usites], 
         time = "time", 
         yfactor = 1e9, 
         cex = 0.5,
         verbose = FALSE)
```

@@

```{r filter}
north <- 80
south <- 10
west <- -170
east <- -50
max_altitude <- 8000
evening <- 14

@@

```{r altitude}
dfa <- df[,
          max(altitude_final),
          by = site_code] |> unique()

@@

```{r addtime}
df2 <- obs_addtime(df)
```
Then we need a *key_time* to aggregate data.
This can be done using UTC, solar, or local time.
The normal approach is using afternoon solar or local time.

@@

```{r st}
df2$solar_time <- obs_addstime(df2)

@@

```{r cut}
df2$solar_time_cut <- cut(x = df2$solar_time,
                          breaks = "1 hour") |>
  as.character()

@@

```{r checkst}
df3 <- df2[hour_st %in% evening]
df3[, c("solar_time", "solar_time_cut")]

@@

```{r keytime}
df3$key_time <- df3$solar_time_cut
```

```{r agg}
df4 <- obs_agg(dt = df3,
               cols = c("value",
                        "latitude",
                        "longitude",
                        "site_utc2lst"),
               verbose = T,
               byalt = TRUE)
```
